### 2018-09-10 analysis/Figueroa/methylation.tex
Update vBsr plot

>>>>

\subsection{Selection of significant gene expression probes using vBsr}
We used Variational Bayesian spike regression (vBsr) \cite{logsdon2012novel} to select gene expression probes that are significantly associated with module methylation profile. vBsr is a penalized Bayesian regression model that uses a spike-and-slab prior to impose sparsity constraint on the regression coefficients. Fast computation were achieved by utilizing mean-field approximation. The algorithm was ran 50 times with random initialization to identify multiple local maxima of lower bound and Bayesian Model Averaging (BMA) was used to produce a unique estimate over all identified models. vBsr defines a test statistic $z_{vb}$ and corresponding p-value. We applied Bonferroni correction to the p-values at $\alpha = 0.05$. Figure \ref{vbsr} shows the $-\log p$ values of the gene probes for modules that have at least one significant hits.

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=\textwidth]{../../figures/Figueroa/vbsr.png}
\caption[Gene expression probes significantly associated with methylation module profile selected by vBsr]{\textbf{Gene expression probes significantly associated with methylation module profile selected by vBsr} The Bonferroni corrected significant level is shown as the dashed lines and the significant hits are annotated with corresponding gene symbol. }
\label{vbsr}
\end{center}
\end{figure}
